### 2014-02-11 classicthesis/Chapters/Introduction.tex
thesis outline

\begin{table}
    \myfloatalign
  \begin{tabularx}{\textwidth}{Xll} \toprule
    \tableheadline{labitur bonorum pri no} & \tableheadline{que vista}
    & \tableheadline{human} \\ \midrule
    fastidii ea ius & germano &  demonstratea \\
    suscipit instructior & titulo & personas \\
    %postulant quo & westeuropee & sanctificatec \\
    \midrule
    quaestio philosophia & facto & demonstrated \\
    %autem vulputate ex & parola & romanic \\
    %usu mucius iisque & studio & sanctificatef \\
    \bottomrule
  \end{tabularx}
  \caption[Autem usu id]{Autem usu id.}
  \label{tab:moreexample}
\end{table}

Ei solet nemore consectetuer nam. Ad eam porro impetus, te choro omnes
evertitur mel. Molestie conclusionemque vel at, no qui omittam
expetenda efficiendi. Eu quo nobis offendit, verterem scriptorem ne
vix.

\begin{lstlisting}[float,caption=A floating example]
for i:=maxint to 0 do
begin
{ do nothing }
end;
\end{lstlisting}

>>>>

\begin{description}
\item[Part II ]{introduces the reader to the basic principles and recent work in the fields of Learning-to-Rank}
\item[Part III ]{describes a short overview work in the field of parallel machine learning and Learning-to-Rank.}
\item[Part IV ]{describes implementation details of the Learning-to-Rank algorithms in the Hadoop framework.}
\item[Part V ]{presents and discusses speed-up results for the implemented Learning-to-Rank methods.}
\item[Part VI ]{summarizes the results. The limitations of our research as well as future research directions in the field are mentioned here.}
\end{description}
